What if you drop that? Modeling children's curiosity about physical interactions

### 2020-02-04 paper/paper.Rmd
writing tower section

```{r object-sets}
shapes = c("bowl","cone","dumbbell","octahedron","pentagon","pipe","pyramid","torus","trig prism")

@@

```{r drop-choice, include=F, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.4, fig.height=2.5, set.cap.width=T, num.cols.cap=1, fig.cap = "Relative frequency of drop object choice as a function of stimulus set."}
ch_cond <- hum %>% 
  group_by(StimSet, DropChoice) %>%
  summarise(n = n()) %>%
  mutate(freq = n / sum(n))

ch_cond$StimSet <- factor(ch_cond$StimSet, levels = c("ba","ca","ab","cb","ac","bc"))
fig_drop <- ggplot(ch_cond, aes(x=StimSet, y=freq, shape=DropChoice, color=DropChoice)) + # , size=n
  geom_point(alpha=.8) +
  scale_shape_manual(values=10:19) +
  #geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
  xlab("Stimulus Set") + ylab("Rate of Drop Object Choice") + ylim(0,.66) + 
  langcog::scale_fill_solarized() + ggthemes::theme_few() + 
  geom_hline(yintercept=.33, lty='dashed') + labs(shape="Object", color="Object")
#print(fig_drop)
```

```{r target-hit, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.4, fig.height=2.5, set.cap.width=T, num.cols.cap=1, fig.cap = "Relative frequency of targeted object as a function of stimulus set."}
hum$Target = hum$DropLocation
ch_cond <- hum %>% 
  filter(Target!="outside") %>%
  group_by(StimSet, Target) %>%
  summarise(n = n()) %>%
  mutate(freq = n / sum(n))

ch_cond$Target <- factor(ch_cond$Target, levels = c(shapes, "space"))
fig_targ_hit <- ggplot(ch_cond, aes(x=StimSet, y=freq, shape=Target, color=Target)) + # , size=n
  geom_point(alpha=.8) +
  scale_shape_manual(values=10:20) +
  #geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
  xlab("Stimulus Set") + ylab("Rate of Target Object Hit") + ylim(0,.66) + 
  langcog::scale_fill_solarized() + ggthemes::theme_few() + 
  geom_hline(yintercept=.33, lty='dashed')
#print(fig_targ_hit)
```

@@

```{r}
require(here)
require(tidyboot)
library(ggplot2)
require(tidyverse)

@@

1. height x continuous age
First we examine tower height as a function of age. Yes we find tower height increases with age.
```{r}
cor.test(hum$height_tallest, hum$age_rounded)
```

```{r}
ch_height <- hum %>% group_by(age_rounded, height_tallest) %>%
  summarise(n = n()) %>%
  mutate(freq = n / sum(n))

@@

2. support x supported (counts)
```{r}
tower = subset(tower, tallest_objects!="" & tallest_objects!="pentagon+octahedron, trig prism") # 5 kids who arranged horizontally and 1 kid chose 2 - exclude
df = data.frame(support=NA, supported=NA, n=NA)
for(s in 1:nrow(tower)) {
  objs = unlist(str_split(tower[s,]$tallest_objects, ", "))
  print(objs)
  for(i in 2:length(objs)) {
    df = rbind(df, cbind(support=objs[i-1], supported=objs[i], n=1))
  }
}
df = na.omit(df)
hm <- df %>% group_by(support, supported) %>% count(N=n()) 
hm %>% ggplot(aes(x=support, y=supported)) + geom_tile(aes(fill=N)) + geom_text(aes(label = N)) +
  scale_fill_gradient(low = "white", high = "steelblue") + ggthemes::theme_few()
```

3. support x supported (probabilities)
pr (supported object | support object)
```{r}
tower = subset(tower, tallest_objects!="" & tallest_objects!="pentagon+octahedron, trig prism") # 5 kids who arranged horizontally and 1 kid chose 2 - exclude
df = data.frame(support=NA, supported=NA, n=NA)
for(s in 1:nrow(tower)) {
  objs = unlist(str_split(tower[s,]$tallest_objects, ", "))
  print(objs)
  for(i in 2:length(objs)) {
    df = rbind(df, cbind(support=objs[i-1], supported=objs[i], n=1))
  }
}
df = na.omit(df)
hm1 <- df %>% 
  group_by(support, supported) %>% 
  summarise(n = n()) %>% 
  group_by(support) %>%
  mutate(freq = n / sum(n))
hm1 %>% ggplot(aes(x=support, y=supported)) + geom_tile(aes(fill=freq)) + geom_text(aes(label = round(freq, 2))) +
  scale_fill_gradient(low = "white", high = "steelblue") + ggthemes::theme_few()
```

4. base and top distribution
```{r}
ch_extremes <- hum %>% 
  group_by(base_tallest) %>% 
  count(N=n()) %>%
  filter(base_tallest!="" & base_tallest!="pentagon+octahedron")

@@

## Baseline Curiosity Policy

@@

>>>>

```{r object-sets}
shapes = c("bowl","cone","dumbbell","octahedron","pentagon","pipe","pyramid","torus","trig prism", "space")

@@

```{r drop-choice, include=F, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.4, fig.height=2.5, set.cap.width=T, num.cols.cap=1, fig.cap = "Relative frequency of drop object choice as a function of stimulus set."}
drop_choice_plot <- function(dat, ymax=.66, shapes_vec) {
  ch_cond <- dat %>% 
    group_by(StimSet, DropChoice) %>%
    summarise(n = n()) %>%
    mutate(freq = n / sum(n))

  ch_cond$StimSet <- factor(ch_cond$StimSet, levels = c("ba","ca","ab","cb","ac","bc"))
  ch_cond$DropChoice <- factor(ch_cond$DropChoice, levels=shapes_vec)
  fig_drop <- ggplot(ch_cond, aes(x=StimSet, y=freq, shape=DropChoice, color=DropChoice)) + # , size=n
    geom_point(alpha=.8) +
    scale_shape_manual(values=10:19) +
    #geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
    xlab("Stimulus Set") + ylab("Rate of Drop Object Choice") + ylim(0,ymax) + 
    langcog::scale_fill_solarized() + ggthemes::theme_few() + 
    geom_hline(yintercept=.33, lty='dashed') + labs(shape="Object", color="Object")
  return(fig_drop)
}

fig_drop <- drop_choice_plot(hum, shapes)
#print(fig_drop)
```

```{r target-hit, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.4, fig.height=2.5, set.cap.width=T, num.cols.cap=1, fig.cap = "Relative frequency of targeted object as a function of stimulus set."}
hum$Target = hum$DropLocation

target_hit_plot <- function(dat, ymax=.66, shapes_vec) {
  ch_cond <- dat %>% 
    filter(Target!="outside") %>%
    group_by(StimSet, Target) %>%
    summarise(n = n()) %>%
    mutate(freq = n / sum(n))

  # need to add "space" as level of Target in human data
  ch_cond$Target <- factor(ch_cond$Target, levels = c(shapes_vec))
  fig_targ_hit <- ggplot(ch_cond, aes(x=StimSet, y=freq, shape=Target, color=Target)) + # , size=n
    geom_point(alpha=.8) +
    scale_shape_manual(values=10:20) +
    #geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
    xlab("Stimulus Set") + ylab("Rate of Target Object Hit") + ylim(0,ymax) + 
    langcog::scale_fill_solarized() + ggthemes::theme_few() + 
    geom_hline(yintercept=.33, lty='dashed')
}
#print(fig_targ_hit)
fig_targ_hit <- target_hit_plot(hum, ymax=.66, shapes)
```

@@

```{r load-tower-data}

@@

ht_age = cor.test(hum$age_rounded, hum$height_tallest)
```

First we examine tower height as a function of age, finding that older children tend to build higher towers `r cor_apa(ht_age, format="rmarkdown", print=F)`.

```{r plot-height-by-age, include=F}
ch_height <- hum %>% group_by(age_rounded, height_tallest) %>%
  summarise(n = n()) %>%
  mutate(freq = n / sum(n))

@@

2. support x supported (counts)
```{r heatmap-support-by-supported-counts}
tower = subset(tower, tallest_objects!="" & tallest_objects!="pentagon+octahedron, trig prism") # 5 kids who arranged horizontally and 1 kid chose 2 - exclude
df = data.frame(support=NA, supported=NA, n=NA)
for(s in 1:nrow(tower)) {
  objs = unlist(str_split(tower[s,]$tallest_objects, ", "))
  print(objs)
  for(i in 2:length(objs)) {
    df = rbind(df, cbind(support=objs[i-1], supported=objs[i], n=1))
  }
}
df = na.omit(df)
hm <- df %>% group_by(support, supported) %>% count(N=n()) 
hm %>% ggplot(aes(x=support, y=supported)) + geom_tile(aes(fill=N)) + geom_text(aes(label = N)) +
  scale_fill_gradient(low = "white", high = "steelblue") + ggthemes::theme_few()
```

3. support x supported (probabilities)
pr (supported object | support object)
```{r heatmap-support-by-supported-probs}
tower = subset(tower, tallest_objects!="" & tallest_objects!="pentagon+octahedron, trig prism") # 5 kids who arranged horizontally and 1 kid chose 2 - exclude
df = data.frame(support=NA, supported=NA, n=NA)
for(s in 1:nrow(tower)) {
  objs = unlist(str_split(tower[s,]$tallest_objects, ", "))
  print(objs)
  for(i in 2:length(objs)) {
    df = rbind(df, cbind(support=objs[i-1], supported=objs[i], n=1))
  }
}
df = na.omit(df)
hm1 <- df %>% 
  group_by(support, supported) %>% 
  summarise(n = n()) %>% 
  group_by(support) %>%
  mutate(freq = n / sum(n))
hm1 %>% ggplot(aes(x=support, y=supported)) + geom_tile(aes(fill=freq)) + geom_text(aes(label = round(freq, 2))) +
  scale_fill_gradient(low = "white", high = "steelblue") + ggthemes::theme_few()
```

4. base and top distribution
```{r base-and-top-objects}
ch_extremes <- hum %>% 
  group_by(base_tallest) %>% 
  count(N=n()) %>%
  filter(base_tallest!="" & base_tallest!="pentagon+octahedron")

@@

## Random Policy

## Noncurious Policy

@@

## Results
```{r load-model-data}
load("../analysis/agent-data/model_data.RData") # md

Shapes = c(sort(unique(md$DropChoice)), "space")

rand_drop <- drop_choice_plot(subset(md, policy=="random"), Shapes)
curio_drop <- drop_choice_plot(subset(md, policy=="curious"), Shapes)
noncurio_drop <- drop_choice_plot(subset(md, policy=="noncurious"), Shapes)

md$Target = md$DropLocation

rand_targ <- target_hit_plot(subset(md, policy=="random"), ymax=1, Shapes)
curio_targ <- target_hit_plot(subset(md, policy=="curious"), ymax=1, Shapes)
noncurio_targ <- target_hit_plot(subset(md, policy=="noncurious"), ymax=1, Shapes)
```

```{r combined-model-fig, fig.env = "figure*", fig.pos = "h", fig.align="center", fig.width=7, fig.height=3.2, set.cap.width=T, num.cols.cap=2, fig.cap = "Relative frequency of objects chosen by each model as objects for dropping (first row), and objects hit as targets (second row; pink dots represent hitting empty space), as a function of target/drop set pairing."}

ggarrange(rand_drop, curio_drop, noncurio_drop, 
          rand_targ, curio_targ, noncurio_targ, ncol=3, nrow=2, 
          labels = c("Random", "Curious", "Noncurious"),
          common.legend=T, legend="bottom")
```
